An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing

### 2019-08-28 20_dataset.tex
redo dataset: smaller table

\begin{table}
\caption{3D models used for validation}\label{dataset_description}
\begin{tabular}{l l l}
Name & Author & License \\
\hline
\href{	https://www.thingiverse.com/thing:26555	}{	AirCasting Air Monitor Casing	} & 	HabitatMap	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:3629434	}{	Air hose splitter	} & 	frizinko	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:1155772	}{	Al Hamra Tower	} & 	TurnerConstructionCompany	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:1498967	}{	canon NP-E3 battery cap	} & 	kosuyoung	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:3567409	}{	David	} & 	Thunk3D	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:3132621	}{	Deck Assembly Tool, Plank Screwing Tool	} & 	PSomeone	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:2920060	}{	Ender 3 Cable Chain	} & 	johnniewhiskey	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:2993875	}{	Ergonomic Hacksaw Handle	} & 	mmOne	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:2513922	}{	Gap measurement tool	} & 	ravm84	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:1673030	}{	G-Clamp fully printable	} & 	johann517	 & 	CC-A	\\
\href{	https://www.youmagine.com/designs/gyroid	}{	Gyroid	} & 	Tim Kuipers	 & 	PD	\\
\href{	https://www.thingiverse.com/thing:1327093	}{	3D Printable Jet Engine	} & 	CATIAV5FTW	 & 	CC-NC	\\
\href{	https://www.thingiverse.com/thing:2752165	}{	Lawn Mower Throttle Replacement	} & 	Spammington	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:2854328	}{	OpenRC F1 Internal gear box mod	} & 	intoxikated	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:3592328	}{	PCB Test Fixture	} & 	JMadison	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:1078865	}{	Pioneer Radio Holder for Ford Focus	} & 	Perugino	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:34596	}{	Replicator Dual Fan Mount	} & 	aubenc	 & 	PD	\\
\href{	https://www.thingiverse.com/thing:3754728	}{	Atuador vers\~ao 2 * actuator version 2	} & 	Caroline Holanda	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:1595179	}{	TE Pocket Operator Hard case	} & 	Salvation76	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:3682303	}{	Screw sizer	} & 	Pierrolalune63	 & 	CC-NC	\\
\href{	http://homepage.tudelft.nl/z0s1z/projects/2017-bone-infill.html	}{	Bone-like optimized infill	} & 	Jun Wu	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:26244	}{	Two-Story Spec House	} & 	pwc-phil	 & 	CC-A	\\
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{3D models used for validation}\label{dataset_description}
\newcommand{\ssize}{\footnotesize}
\begin{tabular}{l l l}
Model Name & Author \\
\hline
\href{https://www.thingiverse.com/thing:26555}{\ssize AirCasting Air Monitor Casing} & \ssize HabitatMap\\
\href{https://www.thingiverse.com/thing:3629434}{\ssize Air hose splitter} & \ssize frizinko\\
\href{https://www.thingiverse.com/thing:1155772}{\ssize Al Hamra Tower} & \ssize TurnerConstructionCompany\\
\href{https://www.thingiverse.com/thing:1498967}{\ssize canon NP-E3 battery cap} & \ssize kosuyoung\\
\href{https://www.thingiverse.com/thing:3567409}{\ssize David} & \ssize Thunk3D\\
\href{https://www.thingiverse.com/thing:3132621}{\ssize Deck Assembly Tool \comment{, Plank Screwing Tool}} & \ssize PSomeone\\
\href{https://www.thingiverse.com/thing:2920060}{\ssize Ender 3 Cable Chain} & \ssize johnniewhiskey\\
\href{https://www.thingiverse.com/thing:2993875}{\ssize Ergonomic Hacksaw Handle} & \ssize mmOne\\
\href{https://www.thingiverse.com/thing:2513922}{\ssize Gap measurement tool} & \ssize ravm84\\
\href{https://www.thingiverse.com/thing:1673030}{\ssize G-Clamp fully printable} & \ssize johann517\\
\href{https://www.youmagine.com/designs/gyroid}{\ssize Gyroid} & \ssize Tim Kuipers\\
\href{https://www.thingiverse.com/thing:1327093}{\ssize 3D Printable Jet Engine} & \ssize CATIAV5FTW\\
\href{https://www.thingiverse.com/thing:2752165}{\ssize Lawn Mower Throttle Replacement} & \ssize Spammington\\
\href{https://www.thingiverse.com/thing:2854328}{\ssize OpenRC F1 Internal gear box mod} & \ssize intoxikated\\
\href{https://www.thingiverse.com/thing:3592328}{\ssize PCB Test Fixture} & \ssize JMadison\\
\href{https://www.thingiverse.com/thing:1078865}{\ssize Pioneer Radio Holder for Ford Focus} & \ssize Perugino\\
\href{https://www.thingiverse.com/thing:34596}{\ssize Replicator Dual Fan Mount} & \ssize aubenc\\
\href{https://www.thingiverse.com/thing:3754728}{\ssize Atuador versão 2 * actuator version 2} & \ssize Caroline Holanda\\
\href{https://www.thingiverse.com/thing:1595179}{\ssize TE Pocket Operator Hard case} & \ssize Salvation76\\
\href{https://www.thingiverse.com/thing:3682303}{\ssize Screw sizer} & \ssize Pierrolalune63\\
\href{http://homepage.tudelft.nl/z0s1z/projects/2017-bone-infill.html}{\ssize Bone-like optimized infill} & \ssize Jun Wu\\
\href{https://www.thingiverse.com/thing:26244}{\ssize Two-Story Spec House} & \ssize pwc-phil\\

\end{tabular}
\end{table}
